---
geometry: "left=2.5cm,right=4cm,top=2.5cm,bottom=2cm"
output: 
  bookdown::pdf_book:
    toc: false
    includes:
     in_header: header.tex
     before_body: title_page.tex
     after_body: appendix.tex
documentclass: article
bibliography: references.bib
#cls: systats.cls
csl: university-of-stuttgart-sowi-standards.csl
link-citations: yes
---

```{r globalchunks, include=FALSE}
# Default Options - kann bei Gebrauch geändert werden
knitr::opts_chunk$set(
  echo = T # Whether to display code along with its results
  , eval = T # Whether to evaluate the code and include its results
  , results = "asis" # this at deafult is in end much more efficient
  , cache = F # Whether to cache results for future renders (efficient!)
  , warning = F # Whether to display errors
  , message = F # Whether to display messages
  , error = F # maybe turn on
  , tidy = F # Whether to reformat code in a tidy way when displaying it
  , fig.width = 6 # plot width at 6
  , fig.height = 4 # plot height at 4
  , fig.align = "left" # plot alignment center
)

options(xtable.comment = FALSE, scipen = 9999)
```


<!-- \onehalfspacing -->
\setstretch{1.5}

\section{Introduction} 


```{r child = '1_intro.Rmd'}
```

\section{Challenges in Measuring Direct Democracy} \label{challenges}

```{r child = '2_challenges.Rmd'}
```

\section{Direct Democracy Data Sources} \label{data}

```{r child = '3_data.Rmd'}
```

\clearpage

\section{Direct Democracy Measurement Approaches} \label{measurement}


```{r child = '4_measurements.Rmd'}
```

\clearpage

\section{Data Wrangling \& Empirical Comparison} \label{empiric}

```{r child = '5_empirical.Rmd'}
```

\clearpage

\section{Conclusion and Future Research} \label{conclusion}

```{r child = '6_conclusion.Rmd'}
```


\setstretch{1}

\clearpage
\newpage


# References

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent
